Tweets

### 2020-05-19 Rmd/tweets-one.Rmd
copied recover_tweets code to .R file

---
title: "Tweets"
author: "Frederick J. Boehm"
date: "4/9/2020"
output: html_document
---

## Goals

1. Write a R script to query twitter streaming api to get 1 percent sample over 5'.
1. Demonstrate how to set up a crontab to execute script every 5'.
1. Verify that crontab approach works by running it on my computer for, say, 15'.
    1. Cautions about twitter databases: deletions and amendments to tweets
1. Examine structure of JSON obtained from api.

## R code to query twitter streaming api

Install `rtweet` package from CRAN.

```{r, eval = FALSE}
install.packages("rtweet")
install.packages("lubridate")
```

## Parse json file

```{r}
library(magrittr)
source("https://gist.githubusercontent.com/JBGruber/dee4c44e7d38d537426f57ba1e4f84ab/raw/ab87bebb8d020c2f96c71a40a483dc96a4c80e54/recover_stream.R")
```

```{r}
tweets <- recover_stream(path = "../data/2020-05-10 12:00:01-tweets.json", verbose = TRUE) 
tweets %>%
  dplyr::select(status_id) %>%
  readr::write_csv(path = "../data/tweets-status-ids-2020-05-10.csv", col_names = FALSE)
```

@@

```{r}
ids <- readr::read_csv("../data/tweets-status-ids-2020-05-10.csv", col_names = FALSE) %>%
  dplyr::rename(status_id = X1) %>%
  dplyr::mutate(status_id = as.character(status_id))
# need multiple calls to get all tweets rehydrated
tweets_rehydrated1 <- rtweet::lookup_tweets(statuses = ids$status_id, 
                                            parse = TRUE)
tweets_rehydrated2 <- rtweet::lookup_tweets(statuses = broken_ids$status_id, parse = TRUE)
tweets_rehydrated <- tweets_rehydrated1 %>%
  dplyr::bind_rows(tweets_rehydrated2)
```

```{r}
# save ids of tweets that we actually used
readr::write_csv(tweets_rehydrated$status_id, path = "../data/2020-05-10-analyzed-tweet-ids.csv", col_names = FALSE)
```

@@

### Colophon

This report was generated on `r Sys.time()` using the following computational environment and dependencies:

```{r colophon, cache = FALSE}
# which R packages and versions?
if ("devtools" %in% installed.packages()) devtools::session_info()
```

The current Git commit details are:

```{r}
# what commit is this file at? 
if ("git2r" %in% installed.packages() & git2r::in_repository(path = ".")) git2r::repository(here::here())  
```

>>>>

```{r}
tweets <- recover_stream(path = "{{tweet_json_file}}", verbose = TRUE) 
tweets %>%
  dplyr::select(status_id) %>%
  readr::write_csv(path = paste0("../data/tweets-status-ids-", "{{date}}", ".csv"), 
                   col_names = FALSE)
```

@@

```{r}
ids <- readr::read_csv(paste0("../data/tweets-status-ids-", "{{date}}", ".csv"), col_names = FALSE) %>%
  dplyr::rename(status_id = X1) %>%
  dplyr::mutate(status_id = as.character(status_id))
tweets_rehydrated1 <- rtweet::lookup_tweets(statuses = ids$status_id, 
                                            parse = TRUE)
tweets_rehydrated2 <- rtweet::lookup_tweets(statuses = broken_ids$status_id, parse = TRUE)
tweets_rehydrated <- tweets_rehydrated1 %>%
  dplyr::bind_rows(tweets_rehydrated2)
```

```{r}
# save ids of tweets that we actually used
readr::write_csv(tweets_rehydrated$status_id, path = paste0("../data/", "{{date}}", "-analyzed-tweet-ids.csv"), col_names = FALSE)
```

@@

```{r}
Sys.sleep(15 * 60) # sleep for 15 minutes to allow api limits to reset
```

### 2020-05-19 Rmd/tweets.Rmd
ignored json files and other data files
switched csl file for citations
copied recover_tweets code to .R file

```{r}
library(magrittr)
source("https://gist.githubusercontent.com/JBGruber/dee4c44e7d38d537426f57ba1e4f84ab/raw/ab87bebb8d020c2f96c71a40a483dc96a4c80e54/recover_stream.R")
```

```{r}
tweets <- recover_stream(path = "../data/2020-05-10 12:00:01-tweets.json", verbose = TRUE) %>%
  dplyr::mutate(status_id = as.character(status_id))
```

## Dehydrate tweets for sharing

```{r}
broken_ids <- readr::read_csv("broken_tweets.txt", col_names = FALSE) %>%
  dplyr::rename(status_id = X1) %>%
  dplyr::mutate(status_id = format(status_id, scientific = FALSE))
readr::write_csv(tibble::tibble(status_id = c(tweets$status_id, broken_ids$status_id)), col_names = FALSE, path = "../data/2020-05-10-status-ids.csv")
```

## Rehydrate tweets by querying Twitter

```{r}
# need multiple calls to get all tweets rehydrated
tweets_rehydrated <- rtweet::lookup_tweets(statuses = tweets$status_id, parse = TRUE)
```

## Prepare document-term matrix from tweet words

```{r}
# create a twitter-specific stop word list
twitter_stop <- tibble::tibble(word = c("https", "http", "t.co"))
remove_reg <- "&amp;|&lt;|&gt;"
# get a list of english language words and names
library(qdapDictionaries) # contains object GradyAugmented
library(tidytext) # get stop_words
```

```{r}
# https://www.tidytextmining.com/topicmodeling.html#library-heist
# https://www.tidytextmining.com/twitter.html
word_counts <- tweets_rehydrated %>% 
  dplyr::filter(lang == "en") %>%
  dplyr::filter(!stringr::str_detect(text, "^RT")) %>%
  dplyr::mutate(text = stringr::str_remove_all(text, remove_reg)) %>%
  tidytext::unnest_tokens(output = word, input = text) %>%
  dplyr::select(status_id, word) %>%
  dplyr::anti_join(stop_words) %>%
  dplyr::anti_join(twitter_stop) %>%
  dplyr::filter(word %in% GradyAugmented) %>%
  dplyr::count(status_id, word, sort = TRUE) %>%
  dplyr::ungroup()
```

```{r}
tweets_dtm <- word_counts %>%
  tidytext::cast_dtm(status_id, word, n)
```

```{r}
tweets_lda <- topicmodels::LDA(tweets_dtm, k = 15)
```

```{r}
tweets_beta <- tidytext::tidy(tweets_lda, matrix = "beta")
```

```{r}
tweets_top_terms <- tweets_beta %>%
  dplyr::group_by(topic) %>%
  dplyr::top_n(10, beta) %>%
  dplyr::ungroup() %>%
  dplyr::arrange(topic, -beta)
```

```{r}
tweets_top_terms %>%
  dplyr::mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot2::ggplot(ggplot2::aes(term, beta, fill = factor(topic))) +
  ggplot2::geom_col(show.legend = FALSE) +
  ggplot2::facet_wrap(~ topic, scales = "free") +
  ggplot2::coord_flip()
```

```{r}
tweets_gamma <- tidytext::tidy(tweets_lda, matrix = "gamma")
tweets_gamma
```

```{r, eval = FALSE}
# too many documents to plot all
tweets_gamma %>%
  dplyr::mutate(title = reorder(document, gamma * topic)) %>%
  ggplot2::ggplot(ggplot2::aes(factor(topic), gamma)) +
  ggplot2::geom_boxplot() +
  ggplot2::facet_wrap(~ document)
```

>>>>

```{r}
library(magrittr)
source("recover_tweets.R")
```

```{r}
date <- c("2020-05-10", "2020-05-11", "2020-05-12", "2020-05-13", "2020-05-14")
tweet_json_file <- c("../data/2020-05-10 12:00:01-tweets.json",
  "../data/2020-05-11 12:00:01-tweets.json", 
  "../data/2020-05-12 12:00:02-tweets.json",
  "../data/2020-05-13 12:00:02-tweets.json", 
  "../data/2020-05-14 12:00:02-tweets.json")
out <- purrr::pmap_dfc(tibble::tibble(date, tweet_json_file),
                       .f = function(date, tweet_json_file){
                         knitr::knit_expand(text = readLines("tweets-one.Rmd"))
                       })
```

## May 10, 2020

`r knitr::knit(text = out[[1]])`

## May 11, 2020

`r knitr::knit(text = out[[2]])`
